Effects of below-ground sink limitation on growth and carbon balance of Eucalyptus seedlings

### 2015-08-21 manuscript/manuscript_pve.Rmd
moved a random file

## Leaf chemistry
Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P < 0.001).  Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).  Leaf starch content in the smallest container was ca. double  that of free seedlings (P=0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).  Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).

@@

\
Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively. Although g~s~ in free seedlings was generally higher than those in containers (Table 2. P=0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration. Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1). Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment. Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 04.5 %) and decreased approximately 3 % across all containers over the experiment duration. This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.

>>>>

## Leaf chemistry
Leaf N % was significantly higher in free seedlings and the largest container volume at the onset of gas exchange measurements (6th week, P < 0.001).  Over the remaining duration of the experiment the smallest container volume had a significant reduction in leaf N % compared to other soil volumes, while free seedlings maintained the highest leaf N % (Table 1, P < 0.001).  Leaf starch content in the smallest container was ca. double  that of free seedlings (P = 0.039), while leaf soluble sugars did not differ across treatments throughout the experiment (Table 1).  Differences in leaf starch between the free seedling and the smallest container were also evident during the first gas exchange campaign (P = 0.001).

@@

\
Neither $\Psi$~pd~ nor $\Psi$~l~ were different across treatments, with mean values of -0.27 and -1.2 MPa across all seedlings, respectively. Although g~s~ in free seedlings was generally higher than those in containers (Table 2. P = 0.001), the mean rates for all seedlings were high at 0.37 mol m^-2^ s^-1^ and did not decline significantly across the experiment duration. Additionally, leaf $\delta$^13^C at final harvest was not different across treatments (Table 1). Combined these indices provide strong evidence that water stress was not apparent on these seedlings throughout the experiment. Soil N % at harvest was not different across soil volumes ($\bar{x}$ = 04.5 %) and decreased approximately 3 % across all containers over the experiment duration. This indicates that nutrient leaching from free seedlings or from draining of containers following natural rainfall events did not differ between treatments.
